---
name: Luke
surname: Barnes
position: "Graduate Student"
address: "22 Wynona Street, Fort Smith, Arkansas"
pronouns: He/Him
phone: (479)353-8597
email: "lb244@uark.edu"
github: lukeblaster9
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Education

```{r}
library(tibble)
library(vitae)

tribble(
  ~Degree, ~Year, ~Institution,
  "**MS in Statistics and Analytics**", "Expected May 2027", "- Univ. of Arkansas",
  "**BA in Biology**", "May 2024", "- Univ. of Arkansas – Fort Smith",
  "**AA With Distinction**", "Dec 2024", "- Univ. of Arkansas – Fort Smith"
) %>%
  detailed_entries(Degree, Year, Institution)
```

# Research Experience

```{r}
library(tibble)
library(vitae)

# Research Experience
research <- tribble(
  ~Position, ~Dates, ~Organization, ~Description,
  
  "Master’s Student in Douglas Lab", "August 2025 - Present",
  "Drs. Michael and Marlis Douglas, University of Arkansas, Fulbright College of Arts and Sciences, Biological Sciences",
  paste(
    "**Forecast Performance of Models of Varying Complexity Applied to Cartilaginous Fish Landings Data**\n",
    "- Obtained and wrangled fisheries landings data of cartilaginous fish from Ministry of Primary Industries (New Zealand governmental entity)\n",
    "- Replicated the procedures detailed in a meta-analysis of forecast performance of models of varying complexity applied to ecological data\n",
    "- Wrote a manuscript describing methods, analysis, and results; currently undergoing initial edits before submission\n\n",
    
    "**Model Selection Analysis and Forecasts of Spiny Dogfish in South Pacific Ocean**\n",
    "- Continued the first project\n",
    "- Performed deeper analysis on why the 'best' model provides best forecasts for Spiny Dogfish\n",
    "- Analyzed covariates that may offer insights\n",
    "- Presented forecasts to guide management of the species\n",
    "- Manuscript not yet begun; plan to begin this semester\n\n",
    
    "**Relationship Between Young-of-Year Class Strength and Reservoir Water Levels**\n",
    "- Collaboration with Arkansas Game and Fish Commission\n",
    "- Currently performing analyses to determine the relationship\n",
    "- Plans to develop a manuscript after analyses are completed"
  )
  ,
  
  "NSF RaMP Mentee/Jones Center Technician", "May 2024 – August 2025",
  "Dr. David Mason; Lisa Giencke, The Jones Center at Ichauway",
  paste(
    "- Designed an experiment to develop a germination protocol for imperiled Lythrum curtissii\n",
    "- Developed a TZ testing protocol for viability tests\n",
    "- Performed a time-to-event analysis to determine optimal germination treatments\n",
    "- Designed and presented two posters and one oral presentation\n",
    "- Wrote a manuscript describing the experiment; currently undergoing final edits before submission"
  )
  ,
  
  "Research Associate", "August 2022 - May 2024",
  "Dr. Ragupathy Kannan, University of Arkansas – Fort Smith, College of Arts and Sciences, Biology Department",
  paste(
    "- Collected and organized data for two research projects\n",
    "- Assisted in data analysis, graphic design of figures, and writing of two research papers\n",
    "- Designed and presented one poster and an oral presentation for one of two research projects"
  )
)

# Render the section with bullets and bold project titles
detailed_entries(
  research,
  Position,
  Dates,
  Organization,
  Description
)
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("C:/Users/lukeb/Downloads/My_Publications.bib") %>%
  arrange(desc(author$family), issued)
```

# Presentations

```{r}
library(tibble)
library(dplyr)
library(vitae)

tribble(
  ~Year, ~Event, ~Presentation, ~Type,
  2026, "Arkansas American Fisheries Society Meeting", 
    "Barnes, Luke & Perez, Logan. “Cartilaginous Fisheries: The Wide Net of Forecast Model Selection” AR AFS Meeting,11 February 2026, Holiday Inn, Russellville, Arkansas.",
    "Poster Session",
  2025, "Center for Plant Conservation National Meeting", 
    "Barnes, Luke. “Germination Requirements of Lythrum curtissii” CPC National Meeting, 8 May 2025, Missouri Botanical Garden, St. Louis, Missouri.",
    "Poster Session",
  2025, "The Jones Center at Ichauway Research Symposium", 
    "Barnes, Luke. “A Preliminary Germination Protocol for the Imperiled Lythrum curtissii” The Jones Center at Ichauway Research Symposium, 21 April 2025, The Jones Center at Ichauway, Newton, Georgia.",
    "Poster Session",
  2024, "Georgia Plant Conservation Alliance", 
    "Barnes, Luke. “Germination Requirements of Rare Plants in Southeast Georgia” GPCA, 5 November 2024, State Botanical Garden of Georgia, Athens, Georgia.",
    "Conference Presentation",
  2024, "Southeastern Partners in Plant Conservation", 
    "Barnes, Luke. “Germination Requirements of Rare Plants in Southeast Georgia” SePPCon, 17 October 2024, Atlanta Botanical Garden, Atlanta, Georgia.",
    "Poster Session",
  2023, "INBRE", 
    "Barnes, Luke. “Least Flycatchers Under Reported in Fall Migration in Arkansas—A Citizen Science Conundrum.” INBRE, 4 November 2023, Hillside Auditorium and Physics Building, Fayetteville, Arkansas.",
    "Poster Session",
  2023, "Fort Smith Public Library", 
    "Barnes, Luke. “Biodiversity 101: How to Create a Biodiverse Backyard!” Fort Smith Public Library, 12 June 2023, Fort Smith Public Library, Fort Smith, Arkansas.",
    "Guest Speaker",
  2023, "University of Arkansas – Fort Smith Research Symposium", 
    "Barnes, Luke. “Least Flycatchers Under Reported in Fall Migration in Arkansas—A Citizen Science Conundrum.” UAFS Research Symposium, 7 April 2023, UAFS Library, Fort Smith, Arkansas.",
    "Conference Presentation",
  2023, "Journal of the Arkansas Academy of Sciences", 
    "Barnes, Luke. “Least Flycatchers Under Reported in Fall Migration in Arkansas—A Citizen Science Conundrum.” JAAS, 1 April 2023, Math and Science Building, Pine Bluff, Arkansas.",
    "Conference Presentation"
) %>%
  brief_entries(
    glue::glue("{Presentation}"),
    Year,
    Type
  )

```

# Honors and Awards

```{r}
library(tibble)
library(vitae)
library(glue)

# Honors and Awards
honors <- tribble(
  ~Year, ~Award, ~Institution, ~Amount,
  2021, "STEM Prestigious Scholarship", "University of Arkansas – Fort Smith", "$27,000",
  2021, "Arkansas Scholar", "State of Arkansas", "$2,000",
  2026, "Graduate School & International Education Travel Grant", "University of Arkansas", "$1,000",
  2023, "2nd place UAFS Annual Essay Competition", "University of Arkansas – Fort Smith", "$250",
  2021, "Chancellor’s List", "University of Arkansas – Fort Smith", NA,
  2021, "Dean’s List", "University of Arkansas – Fort Smith", NA,
  2023, "Student Research Award", "University of Arkansas – Fort Smith, Biology Department", NA
) %>%
  # Combine award name, institution, and amount for display
  mutate(Display = ifelse(is.na(Amount),
                          glue("{Award}, {Institution}"),
                          glue("{Award}, {Institution}, {Amount}")))

# Render the honors/awards
brief_entries(honors, Display, Year)

```

# Professional Experience

```{r}
library(tibble)
library(vitae)
library(glue)

# Professional Experience — reformatted for proper wrapping
professional <- tribble(
  ~Position, ~Dates, ~Organization, ~Description,
  
  "**National Science Foundation RaMP (Woods to Water)**", "May 2024 – May 2025",
  "NSF RaMP",
  paste(
    "- Developed a personal research project on seed germination for Lythrum curtissii"
  ),
  
  "**University of Alabama**", "May 2024 – May 2025",
  "University of Alabama",
  paste(
    "- Worked with UA professors to develop a personal project\n",
    "- Received weekly career development trainings\n",
    "- Spent time working in a UA lab under a professor\n",
    "- Assisted a PhD with Johnson Grass genetics: labeling vials and greenhouse work"
  ),
  
  "**The Jones Center at Ichauway**", "Jun 2024 – Aug 2025",
  "Jones Center at Ichauway",
  paste(
    "- Plant Ecology Field Technician\n",
    "- Scouted rare plants for Seeds of Success and the Jones Center\n",
    "- Identified new and monitored known locations for Jones Center, GA DNR, FL DNR\n",
    "- Performed germination and TZ tests on various plants\n",
    "- Collected and prepared herbarium specimens\n",
    "- Collected rare seeds for GA DNR, FL Plant Rescue, and Jones Center seedbank\n",
    "- Processed seeds: cleaning, labeling, imaging, vacuum sealing\n",
    "- Developed R pipeline for germination data analysis\n",
    "- Programmed and maintained game cameras for seed trap field sites\n",
    "- Repaired and set seed traps/cameras to monitor plant-animal interactions\n",
    "- Processed SD cards and uploaded camera/ARU data\n",
    "- Sorted images by species (mostly birds)\n",
    "- Compiled lists of most common birds and fruiting plants\n",
    "- Created ID pamphlets for quick field identification\n",
    "- Regularly cleaned vehicles"
  ),
  
  "**National Ecological Observatory Network**", "Dec 2024 – Apr 2025",
  "NEON",
  paste(
    "- Field technician\n",
    "- Cleaned tower equipment and maintained surrounding areas\n",
    "- Maintained vehicles and conducted inspections\n",
    "- Measured discharge at wadable streams\n",
    "- Collected surface and groundwater chemistry samples\n",
    "- Analyzed and sorted ground litter for biomass\n",
    "- Filtered/processed soil for root biomass and sorted roots by size\n",
    "- Conducted phenological surveys for plant phenology\n",
    "- Maintained and set ground beetle traps; analyzed contents\n",
    "- Set Sherman traps for small mammals\n",
    "- Set CO2 light traps for mosquito collection\n",
    "- Conducted tick surveys using drag cloths"
  )
)

# Render section
detailed_entries(
  professional,
  Position,
  Dates,
  Organization,
  Description
)
```

# Skills and Certifications

* ACF Freshwater Mussel Certification – August 2024; certified in shell identification in field and lab
* Adept in R
* Adept at performing TZ tests
* Proficient in aquatic field sampling techniques (kick-netting, seining, snorkeling)
* Proficient in dichotomous key use
* Proficient in Field Maps and Survey123

# Professional Memberships

```{r}
library(tibble)
library(vitae)
library(glue)

tribble(
  ~Organization, ~Dates,
  "Arkansas Chapter of the American Fisheries Society", "February 2026 - Present",
  "American Society of Ichthyologists and Herpetologists", "October 2023 - Present"
) %>%
  brief_entries(
    glue("{Organization}"),
    Dates
  )
```

# Community Involvement

```{r}
library(tibble)
library(vitae)

community <- tribble(
  ~Position, ~Dates, ~Organization, ~Description,
  
   "Assistance for Elderly", "2019 – Present",
  "Friend",
  paste(
    "- General maintenance of yards.\n",
    "- Help with chores around house.\n",
    "- Assistance moving furniture.\n",
    "- Assistance setting up decorations for holidays.\n",
    "- Rides to appointments or events."
  ),
  
  "UAFS Student Veteran’s Organization", "2023 – 2024",
  "University of Arkansas – Fort Smith",
  "- Assisted in preparing and cooking food for events.",
  
  "Helping Hands", "2016 – 2020",
  "Grand Avenue Baptist Church",
  paste(
    "- Packed boxes of food and distributed to those in need.\n",
    "- Delivered furniture."
  ),
  
  "Habitat for Humanity", "2018 – 2019",
  "Habitat for Humanity",
  paste(
    "- Built window frames.\n",
    "- Insulated house."
  ),
  
  "Sparks Hospital Volunteen Program", "June 2018 - August 2018",
  "Sparks Hospital",
  paste(
    "- Sanitized stalls.\n",
    "- Sanitized and made beds.\n",
    "- Wheeled patients to vehicles."
  ),
  
  "Ramsey Service Squad", "2017 – 2018",
  "Ramsey Junior High",
  paste(
    "- Held a turkey donation event for Thanksgiving.\n",
    "- Built wreaths for graves of veterans in honor of Veteran’s Day.\n",
    "- Placed wreaths on graves of veterans for Veteran’s Day."
  )
)

# Render the section
detailed_entries(community, Position, Dates, Organization, Description)
```

