---
name: Luke
surname: Barnes
position: "Graduate Student"
address: "22 Wynona Street, Fort Smith, Arkansas"
pronouns: He/Him
phone: (479)353-8597
email: "lb244@uark.edu"
github: lukeblaster9
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution,
  "MS in Statistics and Analytics", "Expected Graduation May 15, 2027", "University of Arkansas",
  "BA in Biology", "May 10, 2024", "University of Arkansas - Fort Smith",
  "AA With Distinction", "December 15, 2024", "University of Arkansas - Fort Smith"
) %>% 
  detailed_entries(Degree, Year, Institution)
```

# Research Experience

```{r}
tribble(
  ~Position, ~Dates, ~Supervisor, ~Organization, ~Description,
  "Master’s Student in Douglas Lab", "August 2025 - Present", 
    "Drs. Michael and Marlis Douglas", 
    "University of Arkansas, Fulbright College of Arts and Sciences, Biological Sciences",
    c(
      "Forecast Performance of Models of Varying Complexity Applied to Cartilaginous Fish Landings Data:",
      "• Obtained and wrangled fisheries landings data of cartilaginous fish from Ministry of Primary Industries (New Zealand governmental entity).",
      "• Replicated procedures from a meta-analysis of forecast performance of models applied to ecological data.",
      "• Wrote a manuscript describing methods, analysis, and results; currently undergoing initial edits before submission.",
      "Model Selection Analysis and Forecasts of Spiny Dogfish in South Pacific Ocean:",
      "• Continued the first project with deeper analysis on why the 'best' model provides best forecasts.",
      "• Analyzed covariates that may offer insights.",
      "• Presented forecasts to guide species management.",
      "• Manuscript not yet begun; plan to begin this semester.",
      "Relationship Between Young-of-Year Class Strength and Reservoir Water Levels:",
      "• Collaboration with Arkansas Game and Fish Commission.",
      "• Currently performing analyses to determine the relationship.",
      "• Plans to develop a manuscript after analyses are completed."
    )
  ,
  "NSF RaMP Mentee/Jones Center Technician", "May 2024 – August 2025",
    "Dr. David Mason; Lisa Giencke", 
    "The Jones Center at Ichauway",
    c(
      "• Designed an experiment to develop a germination protocol for imperiled Lythrum curtissii.",
      "• Developed a TZ testing protocol for viability tests.",
      "• Performed time-to-event analysis to determine optimal germination treatments.",
      "• Designed and presented two posters and one oral presentation.",
      "• Wrote a manuscript describing the experiment; currently undergoing final edits before submission."
    )
  ,
  "Research Associate", "August 2022 - May 2024",
    "Dr. Ragupathy Kannan",
    "University of Arkansas – Fort Smith, College of Arts and Sciences, Biology Department",
    c(
      "• Collected and organized data for two research projects.",
      "• Assisted in data analysis, figure design, and writing of two research papers.",
      "• Designed and presented one poster and an oral presentation."
    )
) %>%
  detailed_entries(Position, Dates, paste(Supervisor, Organization, sep = ", "), Description)
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("C:/Users/lukeb/Downloads/My_Publications.bib") %>%
  arrange(desc(author$family), issued)
```

# Presentations

```{r}
library(tibble)
library(dplyr)
library(vitae)

tribble(
  ~Year, ~Event, ~Presentation, ~Type,
  2025, "Arkansas American Fisheries Society Meeting", 
    "Barnes, Luke & Perez, Logan. “Cartilaginous Fisheries: The Wide Net of Forecast Model Selection” AR AFS Meeting, 8 May 2025, Missouri Botanical Garden, St. Louis, Missouri.",
    "Poster Session",
  2026, "Center for Plant Conservation National Meeting", 
    "Barnes, Luke. “Germination Requirements of Lythrum curtissii” CPC National Meeting, 11 February 2026, Holiday Inn, Russellville, Arkansas.",
    "Poster Session",
  2025, "The Jones Center at Ichauway Research Symposium", 
    "Barnes, Luke. “A Preliminary Germination Protocol for the Imperiled Lythrum curtissii” The Jones Center at Ichauway Research Symposium, 21 April 2025, The Jones Center at Ichauway, Newton, Georgia.",
    "Poster Session",
  2024, "Georgia Plant Conservation Alliance", 
    "Barnes, Luke. “Germination Requirements of Rare Plants in Southeast Georgia” GPCA, 5 November 2024, State Botanical Garden of Georgia, Athens, Georgia.",
    "Conference Presentation",
  2024, "Southeastern Partners in Plant Conservation", 
    "Barnes, Luke. “Germination Requirements of Rare Plants in Southeast Georgia” SePPCon, 17 October 2024, Atlanta Botanical Garden, Atlanta, Georgia.",
    "Poster Session",
  2023, "INBRE", 
    "Barnes, Luke. “Least Flycatchers Under Reported in Fall Migration in Arkansas—A Citizen Science Conundrum.” INBRE, 4 November 2023, Hillside Auditorium and Physics Building, Fayetteville, Arkansas.",
    "Poster Session",
  2023, "Fort Smith Public Library", 
    "Barnes, Luke. “Biodiversity 101: How to Create a Biodiverse Backyard!” Fort Smith Public Library, 12 June 2023, Fort Smith Public Library, Fort Smith, Arkansas.",
    "Guest Speaker",
  2023, "University of Arkansas – Fort Smith Research Symposium", 
    "Barnes, Luke. “Least Flycatchers Under Reported in Fall Migration in Arkansas—A Citizen Science Conundrum.” UAFS Research Symposium, 7 April 2023, UAFS Library, Fort Smith, Arkansas.",
    "Conference Presentation",
  2023, "Journal of the Arkansas Academy of Sciences", 
    "Barnes, Luke. “Least Flycatchers Under Reported in Fall Migration in Arkansas—A Citizen Science Conundrum.” JAAS, 1 April 2023, Math and Science Building, Pine Bluff, Arkansas.",
    "Conference Presentation"
) %>%
  brief_entries(
    glue::glue("{Presentation}"),
    Year,
    Type
  )

```

# Honors and Awards

```{r}
library(tibble)
library(vitae)
library(glue)

tribble(
  ~Year, ~Award, ~Institution, ~Amount,
  2026, "Graduate School & International Education Travel Grant", "University of Arkansas", "$1,000",
  2021, "STEM Prestigious Scholarship", "University of Arkansas – Fort Smith", "$27,000",
  2021, "Arkansas Scholar", "State of Arkansas", "$2,000",
  2023, "2nd place UAFS Annual Essay Competition", "University of Arkansas – Fort Smith", "$250",
  2021, "Chancellor’s List", "University of Arkansas – Fort Smith", NA,
  2021, "Dean’s List", "University of Arkansas – Fort Smith", NA,
  2023, "Student Research Award", "University of Arkansas – Fort Smith, Biology Department", NA
) %>%
  # Combine the award name, institution, and amount for display
  mutate(Display = ifelse(is.na(Amount), glue("{Award}, {Institution}"), glue("{Award}, {Institution}, {Amount}"))) %>%
  brief_entries(
    Display,
    Year
  )

```

# Honors and Awards

```{r}
library(tibble)
library(vitae)
library(dplyr)
library(glue)

tribble(
  ~Position, ~Dates, ~Organization, ~Description,
  
  "National Science Foundation RaMP (Woods to Water)", "May 2024 – May 2025",
    "National Science Foundation",
    c(
      "Developed a personal research project pertaining to a seed germination protocol for a rare plant species (Lythrum curtissii)."
    ),
  
  "University of Alabama", "May 2024 – May 2025",
    "University of Alabama",
    c(
      "Worked with UA professors to develop a personal project.",
      "Received weekly trainings pertaining to career development.",
      "Spent time working under a UA professor in their lab.",
      "Assisted a PhD in their project on Johnson Grass genetics by labeling vials and helping in the greenhouse."
    ),
  
  "The Jones Center at Ichauway", "June 2024 – December 2024; April 2025 – August 2025",
    "The Jones Center at Ichauway",
    c(
      "Plant Ecology Field Technician.",
      "Scouted rare plants for Seeds of Success and the Jones Center.",
      "Identified new and monitored known locations of rare plants for the Jones Center, GA DNR, and FL DNR.",
      "Performed and developed germination and TZ tests on a wide variety of plants.",
      "Collected and prepared specimens for herbarium.",
      "Collected rare seeds for Georgia DNR, Florida Plant Rescue, and the Jones Center seedbank, plus common species for Seeds of Success.",
      "Processed rare seeds for seed banking (cleaning, labeling, imaging, vacuum sealing).",
      "Developed pipeline in R for filtering and wrangling germination data for time-to-event analyses.",
      "Programmed and maintained game cameras for seed trap field sites.",
      "Repaired, maintained, and set seed traps and cameras to collect data on plant-animal interactions and seed dispersal.",
      "Processed SD cards and uploaded data from cameras and autonomous recording units.",
      "Sorted images by species (mostly birds).",
      "Compiled lists of most common bird and fruiting plant species for area phenology.",
      "Created basic ID pamphlets for field identification of fruiting plants.",
      "Regularly cleaned vehicles."
    ),
  
  "National Ecological Observatory Network", "December 2024 – April 2025",
    "National Ecological Observatory Network",
    c(
      "Field technician.",
      "Cleaned tower observation equipment and maintained areas around terrestrial equipment.",
      "Maintained vehicles and conducted regular vehicle inspections.",
      "Measured discharge at wadable streams.",
      "Collected surface water and groundwater samples for chemistry analysis.",
      "Analyzed and sorted ground litter for biomass data.",
      "Filtered/processed soil for root biomass and sorted roots by size class.",
      "Conducted regular phenological surveys for plant phenology.",
      "Maintained and set ground beetle traps, analyzed trap contents.",
      "Set Sherman traps for small mammal surveys.",
      "Set CO2 light traps to collect mosquito populations at field sites.",
      "Conducted tick surveys using drag cloths."
    )
) %>%
  detailed_entries(Position, Dates, Organization, Description)

```

# Skills and Certifications

* ACF Freshwater Mussel Certification – August 2024; certified in shell identification in field and lab
* Adept in R
* Adept at performing TZ tests
* Proficient in aquatic field sampling techniques (kick-netting, seining, snorkeling)
* Proficient in dichotomous key use
* Proficient in Field Maps and Survey123

# Professional Memberships

```{r}
library(tibble)
library(vitae)
library(glue)

tribble(
  ~Organization, ~Dates,
  "Arkansas Chapter of the American Fisheries Society", "February 2026 - Present",
  "American Society of Ichthyologists and Herpetologists", "October 2023 - Present"
) %>%
  brief_entries(
    glue("{Organization}"),
    Dates
  )
```

# Professional Memberships

```{r}
library(tibble)
library(vitae)
library(dplyr)
library(glue)

tribble(
  ~Position, ~Dates, ~Organization, ~Description,
  
  "UAFS Student Veteran’s Organization", "2023 – 2024",
    "University of Arkansas – Fort Smith",
    c(
      "Assisted in preparing and cooking food for events."
    ),
  
  "Assistance for Elderly", "2019 – Present",
    "Community Volunteer",
    c(
      "General maintenance of yards.",
      "Help with chores around house.",
      "Assistance moving furniture.",
      "Assistance setting up decorations for holidays.",
      "Rides to appointments or events."
    ),
  
  "Helping Hands", "2016 – 2020",
    "Community Volunteer",
    c(
      "Packed boxes of food and distributed to those in need.",
      "Delivered furniture."
    ),
  
  "Habitat for Humanity", "2018 – 2019",
    "Community Volunteer",
    c(
      "Built window frames.",
      "Insulated house."
    ),
  
  "Sparks Hospital Volunteen Program", "June 2018 - August 2018",
    "Community Volunteer",
    c(
      "Sanitized stalls.",
      "Sanitized and made beds.",
      "Wheeled patients to vehicles."
    ),
  
  "Ramsey Service Squad", "2017 – 2018",
    "Community Volunteer",
    c(
      "Held a turkey donation event for Thanksgiving.",
      "Built wreaths for graves of veterans in honor of Veteran’s Day.",
      "Placed wreaths on graves of veterans for Veteran’s Day."
    )
) %>%
  detailed_entries(Position, Dates, Organization, Description)
```

